Time slice analyses

### 2017-09-07 analyses/02-time-slice-analyses.Rmd
Small progress toward getting the outputs?

time slicing
-----------------------------------

>>>>

Stratigraphy
-----------------------------------

How to go about that????
Need to collate data ourselves or can we use strap?

```{r, eval = FALSE}

## Run the function for Beck data

slug <- "BeckLee"
metric <- c(sum, variances)
metric.name <- "sumvar"

for (bins in seq_along(c(5,10,15,20))){
 run.all.sims(morphospace, tree, FADLAD, bins, metric, 
              metric.name, inc.nodes = TRUE, slug)
}

slug <- "BeckLee"
metric <- c(median, centroids)
metric.name <- "medcentroid"

for (bins in seq_along(c(5,10,15,20))){
 run.all.sims(morphospace, tree, FADLAD, bins, metric, 
              metric.name, inc.nodes = TRUE, slug)
}
